\TITLE

### 2024-08-12 paper/main.tex
update lose of anonimity in case of dispute

@@

Blockchain-based dispute resolution platforms such as  Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Themis~\cite{mengThemisDecentralizedEscrow2019}, Aragon Court~\cite{AragonWhitepaper2023,aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019} offer a promising direction. These systems could employ a pool of field experts who, in the event of a dispute, would examine the smart contract, proofs ( $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) and providing verdicts. Expert participation and honest adjudication would be encouraged through a system of fees, stakes, and rewards. At the time of writing Kleros is the most successful protocol for the disputes resolution, claiminng to employ 716 jurors and having resolved 1645 disputes.

>>>>

In the event of a dispute, the customer may lose their anonymity due to local policy enforcement that requires identification. To maintain anonymity in the event of a dispute, the anonymous dispute resolution service would have to be used. We discuss this further in section~\ref{sec:decentralised-justice}.

@@

Blockchain-based dispute resolution platforms such as  Kleros~\cite{bergollaKlerosSociolegalCase2022, nappertDecentralizedJusticeReinventing2020, gudkovCrowdArbitrationBlockchain2020}, Themis~\cite{mengThemisDecentralizedEscrow2019}, Aragon Court~\cite{AragonWhitepaper2023,aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019, lingwallShouldCodeBe2019} offer a promising direction. These systems could employ a pool of field experts who, in the event of a dispute, would examine the smart contract, the proofs ( $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) and provide verdicts. Expert participation and honest verdicts are encouraged through a system of fees, stakes and rewards. At the time of writing Kleros is the most successful platform for resolving consumer disputes in e-commerce or collaborative economy. It has received funding from the Commission's European Innovation Council~\cite{CommissionEuropeanInnovation2020}. The protocol claims to have resolved 1645 disputes, employing 716 jurors and rewarding them with 401 ETH. Kleros allows integration with new protocols and we leave it to future work.
